Comprehensive optical and data management infrastructure for high-throughput light-sheet microscopy of whole mouse brains

### 2015-03-25 Neurophotonics/latex-style-files-spie-manuscript/manuscript_snellendo.tex

\section{Representative results}

	\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{data_panel.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:LSMdata} Whole mouse brain tomography. Imaging of whole transgenic mouse brains treated with CLARITY and cleared with TDE 63\% imaged with Olympus, 25X objective. (A) 3D rendering of a parvalbumin-dTomato brain. (B) 3D rendering of stacks from PV-dTomato mouse brain, GAD-dTomato mouse brain,  PI stained mouse brain, scale bar = $400 \micro m$. (C,D,E) High resolution insert, of the stack corresponding to red boxes in C. Scale bar = $100 \micro m$. Modified with permission from \cite{Costantini}.} 
   \end{figure}

Some representative data produced by our microscope are reported in Fig. \ref{fig:LSMdata}. With the apparatus describe in this paper, whole mouse brains can be imaged in their entirety (Fig. \ref{fig:LSMdata}A), maintaining a high quality of the image also while going deep inside the specimen (Figs. \ref{fig:LSMdata}B). The resolution and contrast of the images allow distinguish axonal tracts (Fig. \ref{fig:LSMdata}C) in the brain of a PV-cre-dTomato transgenic mouse, in which parvalbuminergic neurons are fluorescently labeled. GABAergic interneurons can be clearly identified using a GAD2-cre-dTomato mouse (Fig. \ref{fig:LSMdata}D), while nuclear staining with propidium iodide (PI) permits to visualize all the cells (neuronal or not) in the brain. Such whole-brain dataset can be used to localize cellular distribution in three-dimensions using automatic cell-detection software \cite{Frasconi2014}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments
The authors are grateful to Riccardo Ballerini and Ahmed Hajeb from the mechanics workshop at LENS for fabrication of the sample chamber. We further thank Marco De Pas from the electronic workshop for his expertise in the fabrication of the custom-made amplification electronics. We thank GARR for the 10GB optical fibre connection to CINECA and  CINECA for hosting us on PICO.\\ 
The research leading to these results has received funding from the European Union Seventh Framework Program (FP7\slash2007-2013) under grant agreements no. 604102 (Human Brain Project) and n$\degree$ 284464 (LASERLAB-EUROPE). The research has also been supported by the Italian Ministry for Education, University and Research in the framework of the Flagship Project NanoMAX, by  ``Ente Cassa di Risparmio di Firenze" (private foundation). Research activities were also supported by Regione Toscana in the program POR-CreO 2007-2013 (Linea di interventi 1.5.a - 1.6 - Bando Unico R\&S 2012) under grant agreement (CUP) n$\degree$ 6408.30122011.026000201.

@@

\subsubsection{Sample preparation for whole brain imaging}
Mouse brains were processed using the CLARITY protocol \cite{Chung2013} and cleared with a new refractive-index-matching medium \cite{Costantini}. Adult mice (post-natal day 56) were anaesthetized with isoflurane and transcardially perfused with 20 ml ice-cold phosphate-buffered saline (PBS) solution (pH 7.6) followed by 20 ml of a mixture of 4\% (wt/vol) paraformaldehyde (PFA), 4\% (wt/vol) acrylamide, 0.05\% (wt/vol) bis-acrylamide, 0.25\% (wt/vol) VA044 in PBS. We then extracted the brains from the skull and put them in the same PFA/acrylamide/bis-acrylamide/VA044/PBS solution at 4°C for 3 days. Afterwards, we degassed the samples and increased their temperature to 37 °C to initiate polymerization. The embedded samples were then extracted from the gel and washed with clearing solution solution (sodium borate buffer (200 mM, pH 8.5) containing 4\% (wt/vol) sodium dodecyl sulfate) at 37 °C through gentle shaking. To perform electrophoretic tissue clearing (ETC), hydrogel-embedded brains were placed in a custom-built organ-electrophoresis chamber. The same clearing solution was circulated through the chamber and a voltage of 20V was applied across the ETC chamber at 37 °C for several days. After clearing, brains were incubated in PBST0.1 (PBS and 0.1\% Triton X-100, pH 7.6) at 37 °C for 2 days to remove the clearing solution. As a final step, murine brain were incubated in 50 ml of 30\% and 63\% (vol/vol) 2,2'-thiodiethanol in 0.01M PBS (TDE/PBS), each for 1 day respectively at 37°C while gently shaking. The final 63\% TDE/PBS solution has a refractive index $n\simeq 1.45$, allowing for refractive index matching and thus tissue transparency.

>>>>

\section{Data}

	\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{data_panel.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:LSMdata} Whole mouse brain tomography. Imaging of whole transgenic mouse brains treated with CLARITY and cleared with TDE 63\% imaged with Olympus, 25X objective. (A) 3D rendering of a parvalbumin-dTomato brain. (B) 3D rendering of stacks from PV-dTomato mouse brain, GAD-dTomato mouse brain,  PI stained mouse brain, scale bar = $400 \micro m$. (C,D,E) High resolution insert, of the stack corresponding to red boxes in C. Scale bar = $100 \micro m$.} 
   \end{figure}

	To exemplify the imaging capabilities of our microscope see Fig. \ref{fig:LSMdata}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments
The authors are grateful to Riccardo Ballerini and Ahmed Hajeb from the mechanics workshop at LENS for the conception and fabrication of the sample chamber. We further thank Marco De Pas from the electronic workshop for his expertise in the fabrication of the custom-made amplification electronics. We thank GARR for the 10GB optical fibre connection to CINECA and  CINECA for hosting us on PICO. Human Brain Project tutta la vita and also Ludo's long sentence copy pasta.

@@

\subsubsection{Sample preparation for whole brain imaging}
